Behavior Driven Development in Haskell

### 2012-05-23 paper.tex
writing intro.

@@

TBD: Strong type system.

TBD: Tend not to write tests

The purpose of this paper is to
encourage Haskllers to write documentation, which can be used for testing, in their libraries.

@@

>>>>

TBD: Asbtract will be written at the final moment.

@@

One of the best features of Haskell is its strong type system, 
which ensures no type errors in programs if they can be complied.
Thanks to this, programs written in Haskell have less bugs
than other programming languages which do not provide such strong type systems.

Unfortunately, the strong type system of Haskell does not guarantee
no value errors.
Haskellers is, however, apt to rely on the strong type system too much.
They tend to write less test programs than programmers of other
programming languages.

This also means that typical usage examples cannot be found from test programs.
We agree that type signatures are good abstract document but
there are many functions whose behaviors cannot be guessed from
their names and type signatures.

Why do we dislike to write test programs?
It is probably because writing test programs is not fun.
To encourage Haskellers to write more test programs
to detect value errors,
we need a scheme to make writing test programs fun.

For this purpose,
we brought design methods from other programming language communities and
integrated them with a Haskell-original test method.
In particular, we introduced {\tt doctest} and
integrated with QuickCheck. 
We also implemented {\tt hspec} with QuickCheck enabled.

In our method, the text for design takes role of documentation and
is used as test cases. 
This method would motivate Haskellers
bacause it has a kill-three-birds-with-one-stone aspect.

%The purpose of this paper is to encourage Haskllers to write documentation, which can be used for testing, in their libraries.

@@

how to handle error cases.
